### 2021-02-05 README.Rmd
Update README

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/zonebuilders/zonebuilder.svg?branch=master)](https://travis-ci.org/zonebuilders/zonebuilder)
<!-- badges: end -->

@@

```{r install-gh, eval=FALSE}
# install.packages("devtools")
devtools::install_github("robinlovelace/zonebuilder")
```

@@

Zonebuilder works with `sf` objects and works well alongside the `sf` package and visualisation packages that support spatial data such as `ggplot2`, `leaflet`, `mapdeck`, `mapview` and `tmap`, the last of which we'll use in the following maps.
Attaching the package provides the example datasets `london_area` and `london_cent`, the geographic boundary and the centre of London:

>>>>

<!-- badges: start -->
<!-- [![Codecov test coverage](https://codecov.io/gh/zonebuilders/zonebuilder/branch/master/graph/badge.svg)](https://codecov.io/gh/zonebuilders/zonebuilder?branch=master) -->
[![R-CMD-check](https://github.com/zonebuilders/zonebuilder/workflows/R-CMD-check/badge.svg)](https://github.com/zonebuilders/zonebuilder/actions)
<!-- badges: end -->

@@

```{r install-gh, eval=FALSE}
# install.packages("remotes")
remotes::install_github("zonebuilders/zonebuilder")
```

@@

Zonebuilder builds on the `sf` package and works well with mapping packages such as `ggplot2`, `leaflet`, `mapdeck`, `mapview` and `tmap`, the last of which we'll use in the following maps.
Attaching the package provides the example datasets `london_area` and `london_cent`, the geographic boundary and the centre of London:
